### 2021-05-15 response.tex

\begin{mdframed}
\ldots\, Using the SBO to annotate the assumptions seems an odd choice to me.
Looking at Table S1, it seems that the SBO terms are giving a very high level annotation as to the type of model entity mentioned in the assumption, but doesn't provide any semantics about what the assumption is.
Looking at assumptions annotated with SBO:0000009 (kinetic constant), for example, a user can search for assumptions that have something to do with a kinetic constant, but doesn't help to examine if its an assumption based on time scale analysis (e.g., row 3) or perhaps just an assumption that certain behaviour is assumed (e.g., row 13).
I wonder if something like the Evidence and Conclusion Ontology (https://evidenceontology.org/) might provide a source of more meaningful terms to use in annotating assumptions?
I may simply be missing something here, so perhaps a bit more explanation about how the SBO annotations are being used to annotate assumptions would help clarify things (or future work to extend the current work with enriched semantics?). \ldots
\end{mdframed}

You are right.
Using SBO to annotate the (modeling) assumptions only shows which part of the model is being approximated (e.g., the kinetic constant, interactions of molecules, etc.).
We have chosen SBO because it is \enquote{tailored specifically for the kinds of problems being faced in Systems Biology}~\cite{SBOidentifiers}.
%By using SBO, we are trying to answer, which part of the model contains assumptions rather than what was assumed.

We have looked into the \href{https://evidenceontology.org/}{Evidence and Conclusion Ontology (ECO)}.
It is \enquote{describing the various types of evidence that are generated during the course of a scientific study and which are typically used to support assertions made by researchers}~\cite{Chibucos2017}.
When collecting the assumptions made by the authors, the evidence for these has not always become clear to us.
Therefore, we do not feel able to annotate the assumptions using ECO.
We have added a remark on this in the main text (see lines XXX-XXX).
%TODO add line numbers

%Assumptions are naturally lacking broader evidence.
%Therefore, we do not think that this ontology may be more useful for annotating assumptions.

\begin{mdframed}
\ldots\, The authors define a minimal set of PROV-DM entities and activity types they have found useful for capturing provenance information of simulation studies when extracting provenance knowledge from the published literature.
This minimal set does seem sufficient for the Wnt signalling demonstration presented here and the authors briefly explore how this set could be expanded in future.
But I worry that the wet-lab data entity seems under-specified and perhaps less useful than it could be.
While I understand that often in the literature the source of experimental data is not clearly described, with the recent growth of platforms like \url{https://www.protocols.io/} which enable scientists to provide rich descriptions of their protocols in a reusable manner, I wonder if the authors have considered how to incorporate that type of knowledge into their provenance graphs? \ldots
\end{mdframed}

As we have stated in our manuscript, \enquote{we have not included an entity \WE{}.
Our focus is on the result of the \WE{} (i.e., the \WD{}) and its role within the simulation study (e.g., being used in a \BSM{}, \CSM{}, or \VSM{} activity).}
In the future, one could add an entity of type \WE{} as well as corresponding activities describing its generation.
%We have thoroughly thought about further specifying the entity of type Wet-lab Data, by, for example, using more information that is required my the  Minimum Information About a Cellular Assay, and the Cellular Assay (MIACA) guideline~\cite{Wiemann_miaca}.
%We have limited the amount of information we are asking for (i.e., description, reference, type of experiment, organism, organ / tissue / cell line) because we wanted to make it feasible for us to fill out the information for all entities of that type we have found in the Wnt signaling studies.
%At the same time, we know and have argued that our presented class diagram needs eventually to be extended after it has been applied for some time.
We know that information about the experiment itself is very important.
Therefore, we added the possibility to point to the full wet-lab experiment description, for example, by referencing a file on \url{https://www.protocols.io/} or by providing a DOI within the description of a \WD{} entity (see lines xxx--xxx).
%TODO add the line numbers

\begin{mdframed}
\ldots\, Minor comments\\
-{}-{}-{}-{}-{}-{}-{}-{}-{}-{}-{}-{}-{}-\\
It may not be obvious to the reader exactly what PROV is when first mentioned in the abstract. \ldots
\end{mdframed}

We have changed it and hope that it is clearer now.

\begin{mdframed}
\ldots\, The assertion in the abstract that this provenance information is all that is required to answer the question of an "appropriate starting point" is perhaps overstating things.
The provenance information contributes to that answer, but it is not the only knowledge that is required to make an informed decision. \ldots
\end{mdframed}

We have adapted our claim.

\begin{mdframed}
\ldots\, Figure 3 caption: "prociding" - perhaps meant to be providing? \ldots
\end{mdframed}

Fixed.

\begin{mdframed}
\ldots\, I completely agree with the authors that provenance information should be collected during the simulation study, but I wonder if the authors have given any thought to how their WebProv tool could be utilised as part of a typical modelling lifecycle to help encourage modellers to do so?
\end{mdframed}

In our experience, it is best to capture provenance information (semi-)automatically or manually during the modeling (and simulation) process.
We have added a few sentences discussing this matter (see lines xxx--xxx).

%TODO add lines.

\bibliography{bibliography}

\end{document}
